---
title: "2020MCS120003_LabAssignment02"
author: "Amith C A"
date: "06/09/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## DSC513 Lab Assignment 2

06/09/2020

#### 1. What output will the following r code produce?
Code:
```{r echo=TRUE,eval=FALSE}
x<-c(TRUE,FALSE,0L)
typeof(x)
```
#### Ans:
The output will be:
```{r echo=FALSE,eval=TRUE}
x<-c(TRUE,FALSE,0L)
typeof(x)
```
The typeof(),will print the type of c. The output will be "integer".The data type of the c() is integer as '0L' is an element. The L is used to specify the value of 0 as integer.

#### 2. What output will the following r code produce?
Code:
```{r echo=TRUE,eval=FALSE}
TRUE | NA
```
#### Ans:
The output will be :
```{r echo=FALSE,eval=TRUE}
TRUE | NA
```
The **|** is logical pipe which performs the logical OR operation.Performing the logial OR operation on TRUE | TRUE and TRUE | FLASE will give TRUE.

#### 3. Let x be defined as: 
Code:
```{r echo=TRUE,eval=FALSE}
x<-c('0','10','5','20','15','10','0','5')
```
Write an R function that would turn x into a factor whose ordering corresponds to the numerical ordering of x

#### Ans:

```{r echo=TRUE,eval=TRUE}
x<-c('0','10','5','20','15','10','0','5')
 y<-factor(sort(as.numeric(x)),ordered = TRUE)
```
The **numeric()** converts the list x to numeric. The **sort()** sorts the elements in ascending order. The **factor()** function with **ordered=TRUE** creates the factor y in ordered form.

#### 4. In R, if mtcars is a data frame, why does mtcars[1:20] return an error? How does it differ from the similar mtcars[1:20,]?

#### Ans:
When slicing a dataframe using mtcars[1:20] there is condition to select only the rows from 1 to 20 but no mention of what to do with the column. In case of mtcars[1:20,] the rows 1 to 20 will get selected from the data frame mtcars. the **,** after 20 suggests that all the columns have to selected.So it does not throw error.

#### 5. Fix each of the following common data frame subsetting errors in R:
```{r echo=TRUE,eval=FALSE}
mtcars[mtcars$cyl = 4]
mtcars[-1:4]
mtcars[mtars$cyl <= 5]
mtcars[mtcars$cyl == 4| 6,]
```
#### Ans:
*   **mt[mtcars$cyl=4]** code is trying to get the records from mtcars which have value 4 for **cyl** column. 

Corrected code: **mtcars[mtcars$cyl==4,]**

*   **mtcars[-1:4,]** code is trying to print the first 4 rows and all columns excluding the first row. But -1 can only be used with 0,also there should be a **,** to get the correct syntax.So the desired code is.

  Corrected code: **mtcars[2:4,]**

*   **mtcars[mtars$cyl <= 5]** is trying to print all the records in mtcars data frame having the value of cyl column less than or equal to 5.

  Corrected code: **mtcars[mtars$cyl <= 5,]**

*   **mtcars[mtcars$cyl == 4| 6,]** is trying to extract the data from mtcars dataframe which have cyl as 4 or 6.For this we use **c()**.

  Corrected code : **mtcars[mtcars$cyl == c(4,6),]**
  
#### 6. Create the vector (20,19,...,2,1) in R ?

#### Ans:
The output will be :
```{r echo=TRUE,eval=TRUE}
20:1
```

#### 7. Create a 6X10 matrix of random integers in R

#### Ans:
```{r echo=TRUE,eval=TRUE}
x<-matrix(sample(1:100,60,replace=TRUE),nrow=6,ncol=10,byrow=TRUE)
x
```

#### 8. Write a function to find the number of entries in each row of a matrix that are greater than 4.

#### Ans:
```{r echo=TRUE,eval=TRUE}
x<-matrix(sample(1:10,60,replace=TRUE),nrow=6,ncol=10,byrow=TRUE)
x
m<-apply(x,1,function(a){sum(a>4)})
m

```

#### 9.In continuation of the previous question. write a function to find how many rows have exactly two instances of the number 7.

#### Ans:
```{r echo=TRUE,eval=TRUE}
x<-matrix(sample(1:10,60,replace=TRUE),nrow=6,ncol=10,byrow=TRUE)
x
y<-which(apply(x,1,function(a){sum(a==7)==2}))
y

```

#### 10. Create a vector of the values of **$e^x$cos(x)** at x=3,3.1,3.2,.....,6. 
#### Ans:
```{r echo=TRUE,eval=TRUE}
x<-seq(3,6,by=0.1)
x
exp(x)*cos(x)

```
#### 11. Create the following by writing code snippets:

#### Ans:
* $\sum_{i=1}^{100}$($i^3$+4$i^2$)
```{r echo=TRUE,eval=TRUE}
i<-1:100
sum(i^3+4*i^2)

```
* $\sum_{i=1}^{25}$($\frac{2^i}{i}$+$\frac{3^i}{i^2}$)
```{r echo=TRUE,eval=TRUE}
i<-1:25
sum(((2^i)/i)+(3^i)/(i^2))

```

#### 12. Execute the following lines which create two vectors of random integers which are chosen with replecement from the integers 0,1,......, 9999. both vectors have length 250 . The code:
```{r echo=TRUE,eval=FALSE}
set.seed(50)
xVec<-sample(0:999,250,replace=T)
yVec<-sample(0:999,250,replace=T)

```
Suppose x=($x_1$,$x_2$,....,$x_n$) denotes the vector xVec and y =($y_1$,$y_2$,....,$y_n$) denotes the vector yVec.
a. Create the vector ($y_2$-$x_1$,...$y_n$-$x_{n-1}$)

#### Ans:
```{r echo=TRUE,eval=TRUE}
set.seed(50)
xVec<-sample(0:999,250,replace=T)
yVec<-sample(0:999,250,replace=T)
yVec[-1]-xVec[-length(xVec)]
```
b.Calculate
$\sum_{i=1}^{n-1}\frac{e^{-x_i +1}}{x_i + 10}$

#### Ans:
```{r echo=TRUE,eval=TRUE}
set.seed(50)
xVec<-sample(0:999,250,replace=T)
yVec<-sample(0:999,250,replace=T)
sum(exp(-xVec[-1])/(xVec[-length(xVec)]+10))

```
#### 13. This question uses the vectors xVec and yVec created in the previous question and the functions sort,order, mean, sqrt, sum and abs.
a. Pick out the values in yVec which are > 600.

#### Ans:
```{r echo=TRUE,eval=TRUE}
set.seed(50)
xVec<-sample(0:999,250,replace=T)
yVec<-sample(0:999,250,replace=T)
yVec[yVec>600]

```
b. What are the index positions in yVec of the values which are > 600?

#### Ans:
```{r echo=TRUE,eval=TRUE}
set.seed(50)
xVec<-sample(0:999,250,replace=T)
yVec<-sample(0:999,250,replace=T)
which(yVec>600)
```
c. What are the values in xVec which correspond to the values in yVec which are > 600? (By correspond, we mean at the same index positions.)

#### Ans:
```{r echo=TRUE,eval=TRUE}
set.seed(50)
xVec<-sample(0:999,250,replace=T)
yVec<-sample(0:999,250,replace=T)
xVec[yVec>600]
```

d. How many values in yVec are within 200 of the maximum value of the terms in yVec?

#### Ans:
```{r echo=TRUE,eval=TRUE}
set.seed(50)
xVec<-sample(0:999,250,replace=T)
yVec<-sample(0:999,250,replace=T)
 sum( yVec>max(yVec)-200 )
```
e. How many numbers in xVec are divisible by 2? 

#### Ans:
```{r echo=TRUE,eval=TRUE}
set.seed(50)
xVec<-sample(0:999,250,replace=T)
yVec<-sample(0:999,250,replace=T)
sum(xVec%%2==0)
```
f. Sort the numbers in the vector xVec in the order of increasing values in yVec.

#### Ans:
```{r echo=TRUE,eval=TRUE}
set.seed(50)
xVec<-sample(0:999,250,replace=T)
yVec<-sample(0:999,250,replace=T)
xVec[order(yVec)]
```

#### 14. Try exploring the function cumprod() or any other function of your choice to calculate:
1 +$\frac{2}{3}$+($\frac{2}{3}$ $\frac{4}{5}$)+($\frac{2}{3}$ $\frac{4}{5}$ $\frac{6}{7}$ 
)+....+ ($\frac{2}{3}$ $\frac{4}{5}$. . .$\frac{38}{39}$)

#### Ans
```{r echo=TRUE,eval=FALSE}
1+sum(cumprod(seq(2,38,b=2)/seq(3,39,b=2)))
```

#### 15. Consider the continuous function f(x).
Write a function tmpFn which takes a single argument xVec. The function should return the vector of
values of the function f(x) evaluated at the values in xVec.

#### Ans:

```{r echo=TRUE,eval=FALSE}
tmpFn <- function(x)
{
ifelse(x < 0, x^2 + 2*x + 3, ifelse(x < 2, x+3, x^2 + 4*x - 7))
}
a <- seq(-3, 3, len=100)
plot(a, tmpFn(a), type="l")
```

