---
title: "2020MCS120003_LabAssignment03"
author: "Amith C A"
date: "13/09/2020"
output:
  pdf_document: default
  html_document: default
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## 2020MCS120003_LabAssignment03

#### Question 1
### Ans:

```{r  echo=FALSE,eval=TRUE, include=FALSE}
library(ggplot2)
library(dplyr)
library(gapminder)
gapminder_2007<-gapminder %>% filter(year==2007)
gapminder_1962<-gapminder %>% filter(year==1962)
```

```{r  echo=FALSE,eval=TRUE}
ggplot(rbind(gapminder_2007,gapminder_1962),aes(x=gdpPercap,y=lifeExp,color=continent))+geom_point()+facet_grid(continent ~ year)
```

#### Question 2
### Ans:

```{r  echo=FALSE,eval=TRUE}
gapminder_India<-gapminder %>% filter(country=='India') %>% filter(year>=1957) %>% filter(year<=2007)
ggplot(gapminder_India,aes(x=year,y=pop))+geom_point()+scale_y_log10() + scale_x_continuous(breaks = seq(1950, 2010, by = 10))
```

#### Question 3
### Ans:

```{r  echo=TRUE,eval=TRUE}
gapminder%>%
mutate(dollars_per_day=gdpPercap/(365*10^3))
```


#### Question 4
### Ans:

```{r  echo=TRUE,eval=TRUE}
x<-gapminder%>%
filter(country=="United States")%>%filter(year==2007)
rmarkdown::paged_table(x)

```

#### Question 5
### Ans:

```{r  echo=TRUE,eval=TRUE}
x<-gapminder %>%
arrange(gdpPercap)
rmarkdown::paged_table(x)
```


#### Question 6
### Ans:

```{r  echo=TRUE,eval=TRUE}
x<-gapminder %>%
arrange(lifeExp)
rmarkdown::paged_table(x)
```


#### Question 7
### Ans:

```{r  echo=TRUE,eval=TRUE}
x<-gapminder %>%
     filter(year == 1952)
rmarkdown::paged_table(x)
```


#### Question 8
### Ans:

```{r  echo=TRUE,eval=TRUE}
x<-gapminder %>%
     filter(continent == 'Europe')%>% filter(year == 1992) %>%
filter(pop == max(pop))
rmarkdown::paged_table(x)
```


#### Question 9
### Ans:

```{r  echo=TRUE,eval=TRUE}
x<-filter(filter (gapminder,continent == 'Europe',year == 1992),pop==max(pop))
rmarkdown::paged_table(x)
```

#### Question 10
### Ans:

```{r  echo=TRUE,eval=TRUE}
gapminder_2007<- gapminder %>%
     filter(year == 2007)
ggplot(gapminder_2007, aes(x = gdpPercap, y = lifeExp)) +
geom_point() +scale_x_log10()
```

#### Question 11
### Ans:

```{r  echo=TRUE,eval=TRUE}
gapminder_1952 <- gapminder %>%
     filter(year == 1952)
ggplot(gapminder_1952, aes(x = pop, y = lifeExp, color = 'blue')) +
geom_point(color='blue') +scale_x_log10()
```

#### Question 12
### Ans:

```{r  echo=TRUE,eval=TRUE}
ggplot(gapminder,aes(x=pop))+
geom_density()+
scale_x_log10()+ facet_wrap(~year)
```


#### Question 13
### Ans:

```{r  echo=TRUE,eval=TRUE}
gapminder_1962 <- gapminder %>%
     filter(year == 1962)
gapminder_2007 <- gapminder %>%
   filter(year == 2007)
gapminder_2002 <- gapminder %>%
   filter(year == 2002)
gapminder_1967 <- gapminder %>%
   filter(year == 1967)
ggplot(rbind(gapminder_2007,gapminder_1962,gapminder_1967,gapminder_2002),aes(x=pop,y=lifeExp,color=continent))+geom_point()+scale_x_log10()+facet_grid(continent~year)
```

#### Question 14
### Ans:

```{r  echo=TRUE,eval=TRUE}
ggplot(gapminder, aes(x =lifeExp)) +
geom_histogram(bins = 30)
```

#### Question 15
### Ans:

```{r  echo=TRUE,eval=TRUE,warning=FALSE}
ggplot(rbind(gapminder_2007,gapminder_1962),aes(x=gdpPercap,y=lifeExp,color=continent))+geom_point()+geom_smooth(method = "loess")+facet_wrap(~continent)
```

#### Question 16 a)
### Ans:

```{r  echo=TRUE,eval=TRUE}
gapminder %>% filter(year == 2007, country == 'United States')
```


#### Question 16 b)
### Ans:

```{r  echo=TRUE,eval=TRUE}
gapminder %>%
filter(year==1977) %>%filter(country=='Ireland')

gapminder %>%
filter(year==1977) %>%filter(country== 'Brazil')
```


#### Question 17 a)
### Ans:

```{r  echo=TRUE,eval=TRUE}
gapminder_2007 <- gapminder %>%
filter(year == 2007)
ggplot(gapminder_2007, aes(x = pop, y =lifeExp )) +
geom_line()


```
Population is inversely proportional to the life expectancy

#### Question 17 b)
### Ans:

```{r  echo=TRUE,eval=TRUE}

gapminder_2007 <- gapminder %>%
filter(year == 2007)
ggplot(gapminder_2007, aes(x = pop, y =gdpPercap )) +
geom_line()

```

Population and gdpPercap are inversely proportional.

#### Question 18
### Ans:

```{r  echo=TRUE,eval=TRUE}

x<-gapminder %>%
  mutate(lifeExp=12*lifeExp)%>%arrange(lifeExp)%>%
filter(continent=="Americas")%>%filter(year==1962)
rmarkdown::paged_table(x)

```

**Bolivia** has the shortest life expectancy in 1962.

#### Question 19 a)
### Ans:

```{r  echo=TRUE,eval=TRUE}
gapminder_1952<-gapminder %>%
filter(year==1952)
gapminder_1952
```



#### Question 19 b)
### Ans:

```{r  echo=TRUE,eval=TRUE}
ggplot(gapminder_1952,aes(x=pop,y=lifeExp,color=continent))+ geom_point()+scale_x_log10()
```

